1.1: Introduction to Econometrics

### 2019-08-27 static/slides/01-slides.Rmd
Fix treatments in slides

- In clinical trials, .shout[treatment A] was effective for a larger percentage of patients than .whisper[treatment B]

- .whisper[Treatment B] was effective for a higher percentage of patients with *large* stones and a higher percentage of patients with *small* stones

>>>>

- In clinical trials, .shout[treatment B] was effective for a larger percentage of patients than .whisper[treatment A]

- .whisper[Treatment A] was effective for a higher percentage of patients with *large* stones and a higher percentage of patients with *small* stones
